DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2018-01-01 paper/comparison.tex

Our basic approach is to use the same DeepPicar software, and repeat
the experiments in Section~\ref{sec:evaluation} on each hardware
platform and compare the results. 
For Tegra TX2, we have two different system configurations,
which differ in whether TensorFlow is configured to use its GPU or
only the CPU cores. Thus, the total four system configurations are
compared.

@@

Figure~\ref{fig:sys_core} shows the average control loop completion
timing of the four system configurations we tested as a function of
the number of CPU cores used.
First, both the Intel UP and Tegra TX2 exhibit superior performance when
compared with the Raspberry Pi 3. 
When all four CPU cores are used, the Intel UP is 2.53X faster than
the Pi 3, while TX (CPU) and TX (GPU) are 3.6X and 7.6X times faster,
respectively, than the Pi 3. 
As a result, they are all able to satisfy the 50 ms 
WCET by a clear margin,
%%  (in the worst case, the UP Board would 
%% still meet it by $\sim$20 ms) --> where's the data showing this?
and, in case of TX2, 50 Hz or even 100 Hz real-time control is
feasible with the help of its GPU. Another observation is that TX2
(GPU) does not change much, as most of the neural network computation
is done at the GPU.

@@

The Intel UP board and TX2 also perform much better when multiple DNN models
are co-scheduled. Figure~\ref{fig:sys_model} shows the results of the
multi-model co-scheduling experiment. Once again, they can comfortably
satisfy 20 Hz real-time performance for all of the co-scheduled DNN control
loops, and in case of TX 2 (GPU), 100 Hz real-time control is still
feasible. Given that the GPU must be shared among the co-scheduled DNN
models, the result suggests that TX2's GPU has sufficient capacity to
accomodate multiple instances of the DNN model we tested.

@@

Finally, we compare the effect of co-scheduling memory bandwidth
intensive synthetic benchmarks on the DNN control loop timing. 
Figure~\ref{fig:sys_bench} shows the results.
As discussed in 
Section~\ref{sec:eval-memhog}, we observed dramatic execution time
increases, up to 9.4X, in Raspberry Pi 3 as we increased the number of
co-scheduled tasks. We also observe increased control loop execution
timing in Intel Up and TX2, but the degree of the increase is not as
dramatic as the Pi3. Compared to their respective solo timings (i.e.,
the model runs on a single core in isolation), Intel UP suffers up to
2.3X execution time increase; TX2 (CPU) and TX2 (GPU) suffer up to
2.2X and 2.5X increase, respectively. This is somewhat suprising
because Raspberry Pi 3's cores are in-order architecture based while
the cores in Intel Up and NVIDIA TX2 are out-of-order architecture
based, and that the memory intensive tasks on out-of-order cores can
generate more memory traffic. We suspect that this is because the
memory subsystems in the Intel UP and TX2 platforms provide higher
bandwidth and fairness than the memory subsystem of the Pi 3.

Another interesting observation is that TX2 (GPU) also suffers
considerable execution time increase (2.5X) despite the fact that the
co-scheduled synthetic tasks do not utilize the GPU. In other words,
the DNN model has dedicated access to the GPU. This is, however, a
known characteristic of integrated CPU-GPU architectue based
platforms where both CPU and GPU share the same memory
subsystem~\cite{Ali2017}. As a result, TX2 (GPU) fails to meet the
10ms deadline for 100 Hz control that would have been feasible if
there was no contention between the CPU cores and the GPU.

>>>>

Our basic approach is to use the same DeepPicar software, and repeat
the experiments in Section~\ref{sec:evaluation} on each hardware
platform and compare the results. 
For the Jetson TX2, we have two different system configurations,
which differ in whether TensorFlow is configured to use its GPU or
only the CPU cores. Thus, the total four system configurations are
compared.

@@

Figure~\ref{fig:sys_core} shows the average control loop completion
timing of the four system configurations we tested as a function of
the number of CPU cores used.
First, both the Intel UP and Jetson TX2 exhibit superior performance when
compared with the Raspberry Pi 3. 
When all four CPU cores are used, the Intel UP is 2.53X faster than
the Pi 3, while the TX2 (CPU) and TX2 (GPU) are 3.6X and 7.6X times faster,
respectively, than the Pi 3. 
As a result, they are all able to satisfy the 50 ms 
WCET by a clear margin,
%%  (in the worst case, the UP Board would 
%% still meet it by $\sim$20 ms) --> where's the data showing this?
and, in case of TX2, 50 Hz or even 100 Hz real-time control is
feasible with the help of its GPU. Another observation is that TX2
(GPU) does not change much, as most of the neural network computation
is done at the GPU.

@@

The Intel UP board and Jetson TX2 also perform much better when multiple DNN models
are co-scheduled. Figure~\ref{fig:sys_model} shows the results of the
multi-model co-scheduling experiment. Once again, they can comfortably
satisfy 20 Hz real-time performance for all of the co-scheduled DNN control
loops, and in the case of the TX2 (GPU), 100 Hz real-time control is still
feasible. Given that the GPU must be shared among the co-scheduled DNN
models, the results suggest that the TX2's GPU has sufficient capacity to
accomodate multiple instances of the DNN model we tested.

@@

Finally, we compare the effect of co-scheduling memory bandwidth
intensive synthetic benchmarks on the DNN control loop timing. 
Figure~\ref{fig:sys_bench} shows the results.
As discussed in 
Section~\ref{sec:eval-memhog}, we observed dramatic execution time
increases, up to 9.4X, in Raspberry Pi 3 as we increased the number of
co-scheduled tasks. We also observe increased control loop execution
timing in the Intel Up and Jetson TX2, but the degree of the increase is 
not as dramatic as the Pi 3. Compared to their respective solo timings 
(i.e., the model runs on a single core in isolation), Intel UP suffers up to
2.3X execution time increase; TX2 (CPU) and TX2 (GPU) suffer up to
2.2X and 2.5X increases, respectively. This is somewhat suprising
because the Raspberry Pi 3's cores are in-order architecture based while
the cores in the Intel Up and NVIDIA TX2 are out-of-order architecture
based, and that the memory intensive tasks on out-of-order cores can
generate more memory traffic. We suspect that this is because the
memory subsystems in the Intel UP and TX2 platforms provide higher
bandwidth and fairness than the memory subsystem of the Pi 3.

Another interesting observation is that the TX2 (GPU) also suffers
considerable execution time increase (2.5X) despite the fact that the
co-scheduled synthetic tasks do not utilize the GPU. In other words,
the DNN model has dedicated access to the GPU. This is, however, a
known characteristic of integrated CPU-GPU architectue based
platforms where both CPU and GPU share the same memory
subsystem~\cite{Ali2017}. As a result, the TX2 (GPU) fails to meet the
10ms deadline for 100 Hz control that would have been feasible if
there was no contention between the CPU cores and the GPU.

### 2018-01-01 paper/evaluation.tex

In comparison, NVIDIA's DAVE-2 system, which has the exact same neural
network architecture, reportedly runs at 30 Hz~\cite{Bojarski2016},
just a bit faster than the DeepPicar. Although we believe it was not
limited by their computing platform (we will experimentally compare
performance differences among multiple embedded computing platforms,
including NVIDIA's Jetson TX2, later in
Section~\ref{sec:comparison}), the fact that the low-cost
Raspberry Pi 3 can achieve similar real-time control performance is
surprising.

@@

Figure~\ref{fig:perf-vs-corecnt} shows the average execution time of
the control loop as we vary the number of cores used by
TensorFlow. As expected, as we assign more cores, the average execution
time decreases---from 61.96 ms on a single core to 42.67 ms on four
cores (a 30\% improvement). However, the improvement is far from ideal
linear scaling. In particular, from 2 cores to 3 cores, the
improvement is mere 2.38 ms (or 4\%). In short, we find that the
scalability of DeepPicar's deep neural network is not ideal on the
platform. We do not know whether it is due to the limitations of
TensorFlow's multicore implementation or if it's the model's inherent
characteristics.

>>>>

In comparison, NVIDIA's DAVE-2 system, which has the exact same neural
network architecture, reportedly runs at 30 Hz~\cite{Bojarski2016}, which 
is just a bit faster than the DeepPicar. Although we believe it was not
limited by their computing platform (we will experimentally compare
performance differences among multiple embedded computing platforms,
including NVIDIA's Jetson TX2, later in
Section~\ref{sec:comparison}), the fact that the low-cost
Raspberry Pi 3 can achieve similar real-time control performance is
surprising.

@@

Figure~\ref{fig:perf-vs-corecnt} shows the average execution time of
the control loop as we vary the number of cores used by
TensorFlow. As expected, as we assign more cores, the average execution
time decreases---from 61.96 ms on a single core to 42.67 ms on four
cores (a 30\% improvement). However, the improvement is far from an ideal
linear scaling. In particular, from 2 cores to 3 cores, the
improvement is mere 2.38 ms (or 4\%). In short, we find that the
scalability of DeepPicar's deep neural network is not ideal on the
platform. We do not know whether it is due to the limitations of
TensorFlow's multicore implementation or if it's the model's inherent
characteristics.
